---
title: "Lab 0 - Hello R!"
author: "Joanne Chae"
date: "Jan 17, 2023"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(datasauRus)
```

## Exercise 1

The data frame has 1846 rows and 3 columns. The 3 variables are dataset, x, and y\

## Exercise 2

```{r}
#| label: plot-dino
dino_data <- datasaurus_dozen |>
  filter(dataset == "dino")
  ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r}
#| label: cor-dino
dino_data |>
  summarize(r = cor(x, y))
```

## Exercise 3

```{r}
#| label: plot-circle
dino_data <- datasaurus_dozen |>
  filter(dataset == "circle")
  ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r}
#| label: cor-circle
dino_data |>
  summarize(r = cor(x, y))
```

While the r value in the correlation coefficient between x and y for the "dino" dataset is -0.0645, it is -0.0683 for the "circle" dataset.

## Exercise 4

```{r}
#| label: plot-star
dino_data <- datasaurus_dozen |>
  filter(dataset == "star")
  ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r}
#| label: cor-star
dino_data |>
  summarize(r = cor(x, y))
```

While the r value in the correlation coefficient between x and y for the "dino" dataset is -0.0645, it is -0.063 for the "star" dataset.

## Exercise 5

(Add a labeled code chunk and narrative here. Insert code chunks using the "insert chunk" button (a green C with a +). Alternatively, use CMD + OPTION + I (Mac) or CTRL + ALT + I (Windows).)
